Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 submission/paper-submission.tex
added tex files
updated the submission folder with the current version of the paper (but will need to be updated again)

{\centering \includegraphics[width=6.5in]{figure/figure-01-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-02-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-03-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-04-1}

@@

{\centering \includegraphics[width=3.125in]{figure/figure-05-1}

@@

{\centering \includegraphics[width=3.125in]{figure/figure-06-1}

@@

{\centering \includegraphics[width=3.25in]{figure/figure-07-1}

@@

In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures). The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.

@@

{\centering \includegraphics[width=2.25in]{./figure-static/figure-08-1}

@@

{\centering \includegraphics[width=3.125in]{figure/figure-09-1}

@@

{\centering \includegraphics[width=6.5in]{./figure-static/figure-10-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-11-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-12-1}

@@

{\centering \includegraphics[width=6.25in]{figure/figure-13-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}

@@

{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}

@@

{\centering \includegraphics[width=3.125in]{figure/figure-C3-1}

>>>>

{\centering \includegraphics[width=6.5in]{figure-01-1}

@@

{\centering \includegraphics[width=6.5in]{figure-02-1}

@@

{\centering \includegraphics[width=6.5in]{figure-03-1}

@@

{\centering \includegraphics[width=6.5in]{figure-04-1}

@@

{\centering \includegraphics[width=3.125in]{figure-05-1}

@@

{\centering \includegraphics[width=3.125in]{figure-06-1}

@@

{\centering \includegraphics[width=3.25in]{figure-07-1}

@@

In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures). \kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83436 land-to-land comparisons.

@@

{\centering \includegraphics[width=2.25in]{figure-08-1}

@@

{\centering \includegraphics[width=3.125in]{figure-09-1}

@@

{\centering \includegraphics[width=6.5in]{figure-10-1}

@@

{\centering \includegraphics[width=6.5in]{figure-11-1}

@@

{\centering \includegraphics[width=6.5in]{figure-12-1}

@@

{\centering \includegraphics[width=6.25in]{figure-13-1}

@@

{\centering \includegraphics[width=6.5in]{figure-B1-1}

@@

{\centering \includegraphics[width=6.5in]{figure-B2-1}

@@

{\centering \includegraphics[width=3.125in]{figure-C3-1}
